---
title: "Natalies work ethic"
author: "ME"
output: 
  revealjs::revealjs_presentation:
    theme: league
  #html_document:
    #toc: TRUE
---

## To start with

We see below, a simple graph of the amount of effort Nat puts in per day, to the amount of pay Nat will receive:

***

``` {r someGraph, echo=F, visible=F}
library(data.table, quietly = T)
library(ggplot2, quietly = T)
library(cowplot, quietly = T, warn.conflict=F)
library(scales, quietly = T)
d <- data.table(work_amount=seq(8, 10, 0.02), amount_of_pay_per_year=(exp(seq(2, 6, 0.04)) + 50) * 1000)
ggplot(d, aes(work_amount, amount_of_pay_per_year)) +
  geom_line(color='red') +
  scale_y_continuous(labels = dollar_format()) +
  labs(x = 'Amount of work per day', y='Amount of pay per year in future')
```

## Bullet Points

Lets test some bullet points:  

- point 1
- point 2
- point 3

## Incremental Bullet Points

Lets test some bullet points:  

> - point 1
> - point 2
> - point 3

## But also...

Now what does the amount of effort Nat puts in per day, look like compared to the amount of sleep Nat gets:

``` {r anotherGraph, echo=F}
library(data.table, quietly = T)
library(ggplot2, quietly = T)
library(cowplot, quietly = T, warn.conflict=F)
d <- data.table(work_amount=seq(8, 10, 0.2), hours_of_sleep=seq(8, 6, -0.2))
ggplot(d, aes(work_amount, hours_of_sleep)) +
  geom_line(color='blue') +
  labs(x = 'Amount of work per day', y='Hours of sleep per day')
```
